---
title: "Lab 07 - Modelling course evaluations"
author: "Conor O'Shea"
date: "`r Sys.Date()`"
output: html_document
---

### Packages and Data

```{r load-packages, message=FALSE, echo=TRUE}
library(tidyverse)
library(tidymodels)

```


```{r read-data}
evals<-read.csv("data/evals.csv", row.names=1)

view(evals)
```


# Exercise 1: Exploratory Data Analysis

1.  Visualize the distribution of `score` in the dataframe `evals`.

```{r viz-score}

visDist <- evals %>%
  ggplot(aes(x = score)) +
  geom_histogram()+
  labs(x = "Score", y = NULL)

print(visDist)
```

``` {r summary-stats}

# mean score (is on higher end)
meanScore <- evals %>%
  summarize(meanScore = mean(score, na.rm = TRUE))


# median score (shows where global max lies)

medianScore <- evals %>%
  summarize(medianScore = median(score,na.rm = TRUE))

print(meanScore)
print(medianScore)



```

*Skewed distrubution on higher end of score. Tells use that students rate most courses highly. Expected to see this since good school. *

2.  Visualize and describe the relationship between `score` and `bty_avg` using `geom_point()` to represent the data. 

```{r scatterplot}
# Using geom_point()

geomPointPlot <- evals %>%
  ggplot(aes(x = bty_avg, y = score)) +
  geom_point() +
  ggtitle("Scatter Plot using geom_point") +
  xlab("Average beauty score of prof") +
  ylab("score of course")

print(geomPointPlot)

geomJitterPlot <- evals %>%
  ggplot(aes(x = bty_avg, y = score)) +
  geom_jitter() +
  ggtitle("Scatter Plot using geom_point") +
  xlab("Average beauty score of prof") +
  ylab("score of course")

print(geomJitterPlot)
```

*Beauty score of prof doesn't have an effect as average score is high throughout all x-values, however there are more points to left as whole, therefore there are more ugly professors in the school/uni. *

*Jitter mitigates overlap of points by inserting more points around existing  points. I*

# Exercise 2: Simple Linear regression with a numerical predictor

1. Fit a linear model called `score_bty_fit` to predict average professor evaluation `score` from average beauty rating (`bty_avg`). Print the regression output using `tidy()`.

```{r fit-score_bty_fit, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_fit <- evals %>%
  ggplot(aes(x = bty_avg, y = score)) +
  geom_point() +
  geom_smooth(method = "lm", 
              se = FALSE) +
  labs(
    title = "Predicted score due to beauty rating",
    subtitle = "Texas teacher attractiveness survey",
    x = "Average beauty rating (out of 5)",
    y = "Score"
  )

print(score_bty_fit)
```

```{r tidy-score_bty_fit, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
tidy(___)
```

*Add your linear model here. Don't worry too much about notation, you can use things like score-hat.*

2. Plot the data again using `geom_jitter()`, and add the regression line.

```{r viz-score_bty_fit,eval=FALSE}
# add your plot here. Hint, you can add the regression line using geom_smooth()
```

3. Interpret the slope of the linear model in context of the data.

*Add your interpretation here*

4. Interpret the intercept of the linear model in context of the data. Comment on whether or not the intercept makes sense in this context.

*Add your interpretation here*

5. Determine the $R^2$ of the model and interpret it in the context of the data.

```{r R2, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(___)$___
```

*Add your interpretation here*

6. Make a plot of residuals vs. predicted values for the model above.

```{r viz-score_bty_fit-diagnostic, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_aug <- augment(score_bty_fit$fit)

ggplot(___) + ...
```

# Exercise 3: Simple Linear regression with a categorical predictor

0. Look at the variable rank, and determine the frequency of each category level.

```{r}
# ... 
```

1. Fit a new linear model called `score_rank_fit` to predict average professor evaluation `score` based on `rank` of the professor.

```{r fit-score_rank_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

2. Fit a new linear model called `score_gender_fit` to predict average professor evaluation `score` based on `gender` of the professor. 

```{r fit-score_gender_fit}
# fit model

# tidy model output
```

```{r score_gender_intercept, eval=FALSE}
# remove eval = FALSE from the code chunk options
score_gender_intercept <- tidy(score_gender_fit) %>% 
  filter(term == "(Intercept)") %>%
  select(estimate) %>%
  pull()
```

```{r score_gender_slope, eval=FALSE}
# remove eval = FALSE from the code chunk options
score_gender_slope <- tidy(score_gender_fit) %>% 
  filter(term == "gendermale") %>%
  select(estimate) %>%
  pull()
```

*Add your narrative here. Use in-line code!*

# Exercise 4: Multiple linear regression

1. Fit a multiple linear regression model, predicting average professor evaluation `score` based on average beauty rating (`bty_avg`) and `gender.`

```{r fit-score_bty_gender_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

```{r eval = FALSE}
ggplot(___) + ...
```

2. What percent of the variability in `score` is explained by the model `score_bty_gender_fit`. 

```{r}
# ...
```


3. What is the equation of the line corresponding to just male professors?

*Add your equation here.*

4. For two professors who received the same beauty rating, which gender tends to have the higher course evaluation score?

*Add your narrative here.*

5. How does the relationship between beauty and evaluation score vary between male and female professors?

*Add your narrative here.*

6. How do the adjusted $R^2$ values of `score_bty_fit` and `score_bty_gender_fit` compare? 

```{r eval=FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(___)$adj.r.squared
glance(___)$adj.r.squared
```

*Add your narrative here.*

7. Compare the slopes of `bty_avg` under the two models (`score_bty_fit` and `score_bty_gender_fit`).

*Add your narrative here.*

# Exercise 5: Interpretation of log-transformed response variables

If you do not know how to use LaTeX, do this exercise with pen and paper.
